Methodology for Assessing the State of the Practice for Domain X

### 2020-11-12 StateOfPractice/Methodology/Methodology.tex
updated introduction section 1 methodology, added performance benchmark note

\pmi{comment from meeting: remove performance benchmarks from scope of exercise
  because enough other people consider this. Add similar comment into
  introduction explaining (link to examples of performance considered elsewhere
  in similar projects??) why performance is not considered} \pmi{do we have
  specific examples of other works considering performance benchmarks?}

The scope of this document is to conduct a current state of practice analysis of
software in a scientific computing domain for the purpose of understanding
quality and assisting in future development. We leave the assessment of
performance of such software to other similar projects. The methodology
presented here is part of an overall assessment of the impact of model driven
engineering and code generation on the sustainability of scientific computing
software. The research proposal for this assessment, which contains a more
detailed description of this state of practice exercise, can be found
\href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ResearchProposal.pdf}{here}. The
research questions that this exercise will answer are found in Section
\ref{ResearchQuestions}. Section \ref{StepsAQDS} outlines the steps to be taken.

Note the following formatting conventions of this document. \textcolor{red}{Red}
text denotes a link to information within this document. \textcolor{cyan}{Cyan}
text denotes a URL link.

>>>>

The scope of this document is to conduct a current state of practice analysis of
software in a scientific computing domain for the purpose of understanding
quality and assisting in future development. We observe product, artifact, and process quality in our analysis. We leave the assessment of scientific computing software using performance benchmarks to other projects, such as the work of \cite{kaagstrom1998gemm}. The methodology presented here is part of an overall assessment of the impact of model driven engineering and code generation on the sustainability of scientific computing software. The research proposal for this assessment, which contains a more detailed description of this state of practice exercise, can be found \href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ResearchProposal.pdf}{here}. The
research questions that this exercise will answer are found in Section
\ref{ResearchQuestions}. Section \ref{StepsAQDS} outlines the steps to be taken.

Note the following formatting conventions of this document. \textcolor{red}{Red}
text denotes a link to sections of this document. \textcolor{cyan}{Cyan}
text denotes a URL link. \textcolor{blue}{Blue} text denotes a citation.
